Apparent preferences for cognitive effort fade when multiple forms of effort

### 2020-12-02 Cost_manuscript.Rmd
tweak to modeling criteria

  We performed model comparisons to identify qualities that explained findings from both experiments. Based on the observed choice behavior, an adequate model had to meet seven criteria: 1) show deviations from optimality that were not simply due to overharvesting 2) keep track of recent offer history; 3) experience a slight reduction of acceptances in effortful conditions; 4) persistently display higher acceptances for cognitive effort when faced with single behavioral costs; 5) initially match this preference for cognitive effort trials when foraging for demands and rewards; 6) display a disappearance of this preference as acceptances decreased to a common rate across costs; and 7) not be affected by block order effects. These conditions discarded a number of popular explanatory candidates that were not modeled, such as learned industriousness, boredom, fatigue, sunk cost effects, or asymmetric learning of environmental richness (see Discussion).

@@

  (**hold off on this paragraph until modeling is done**) We do not discard the influence of these elements in daily effort evaluations. Instead, we computationally highlight that effort can became valuable by shortening the subjective elapsed time of trials, a perception that could be recalibrated as individuals experienced multiple forms of demands (Cognitive effort gained value by making trials feel shorter). Alterations in subjective time sensitivity have been shown to play a role in temporal discounting [@Mckerchar2009], and are often experienced when we are fully immersed in a task [@Csikszentmihalyi2014]. The shorter time sensitivity of cognitive effort could be due to its constant recruitment of working memory, impeding estimations of the nominal time, or because of the discrete nature of the task (versus a continuous configuration of the physical and wait tasks). These results expand our understanding of the attractiveness of effort, bringing forth outcome-independent features that can be leveraged to motivate effort engagement in diverse everyday scenarios. ....This could be because: 1) discrete nature of cog taska llowed for counting; 2) flow; 3) persistent recruitment of working memory (Buhi and Gershman). Talk about future experiments: if this is subjective time, changing the pacing of the tasks should change the acceptance rates for cognitive effort. Maybe use this example: if I ask you to perform an activity until you think a minute has elapsed, that estimate will be noisy, but also different for different tasks. That's how it is in real life.

>>>>

  We performed model comparisons to identify qualities that explained findings from both experiments. Based on the observed choice behavior, an adequate model had to meet seven criteria: 1) show deviations from optimality that were not simply due to overharvesting; 2) keep track of recent offer history; 3) experience a slight reduction of acceptances in effortful conditions in the between-subjects experiment; 4) persistently display higher acceptances for cognitive effort when faced with single behavioral costs; 5) initially match this preference for cognitive effort trials when foraging for demands and rewards; 6) display a disappearance of this preference as acceptances decreased to a common rate across costs; and 7) preference ranks should be robust to block order effects, but the magnitude of the differences should be lower for those who started with the physical effort block. These conditions discarded a number of popular explanatory candidates that were not modeled, such as learned industriousness, boredom, fatigue, sunk cost effects, or asymmetric learning of environmental richness (see Discussion).

@@

  (**hold off on this paragraph until modeling is done**) We do not discard the influence of these elements in daily effort evaluations. Instead, we computationally highlight that effort can became valuable by shortening the subjective elapsed time of trials, a perception that could be recalibrated as individuals experienced multiple forms of demands (Cognitive effort gained value by making trials feel shorter). Alterations in subjective time sensitivity have been shown to play a role in temporal discounting [@Mckerchar2009], and are often experienced when we are fully immersed in a task [@Csikszentmihalyi2014]. The shorter time sensitivity of cognitive effort could be due to its constant recruitment of working memory, impeding estimations of the nominal time, or because of the discrete nature of the task (versus a continuous configuration of the physical and wait tasks). These results expand our understanding of the attractiveness of effort, bringing forth outcome-independent features that can be leveraged to motivate effort engagement in diverse everyday scenarios. ....This could be because: 1) discrete nature of cog taska llowed for counting; 2) flow; 3) persistent recruitment of working memory (Buhi and Gershman). Mention that order effects reflect the gradual integration of subjective time across demands in exp 2. Talk about future experiments: if this is subjective time, changing the pacing of the tasks should change the acceptance rates for cognitive effort. Maybe use this example: if I ask you to perform an activity until you think a minute has elapsed, that estimate will be noisy, but also different for different tasks. That's how it is in real life.
